---
title: "Index.Rmd"
author: "Evelyn Sun"
date: "5/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Our domain of interests primarily focus on datasets related to college life. We found three datasets before which included college-tuition dataset, college-basketball dataset and college-majors dataset. 

Basically we're interested in this aspect because they are somehow connnected with our school life. By researching and analyzing those data, it is a great opportunity for us to have a more well-rounded understanding with regard to this. 

Finally, by considering the details of three datasets. We choose the college-tuition data set as our main reasearch emphases. This dataset is both easy understanding and has sufficient data numbers, which makes it more reliable. 


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.