---
title: "Index.Rmd"
author: "Evelyn Sun "
date: "5/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("scripts/function.R")
source("scripts/chart1.R")
source("scripts/chart2.R")
source("scripts/chart3.R")
```

## Introduction
Our domain of interests primarily focus on datasets related to college life. We found three datasets before which included college-tuition dataset, college-basketball dataset and college-majors dataset. 

Basically we're interested in this aspect because they are somehow connnected with our school life. By researching and analyzing those data, it is a great opportunity for us to have a more well-rounded understanding with regard to this. 

Finally, by considering the details of three datasets. We choose the college-tuition data set as our main reasearch emphases. This dataset is both easily understandable and has sufficient data, which makes this dataset more reliable.  


## Summary Information
Here is the summary information we got from our data: 
```{r, echo=FALSE}
df <- read.csv("data/tuition_cost.csv", stringsAsFactors = FALSE)
get_summary_info(df)
ret <- get_summary_info(df)
```
Based on the college-tuition dataset, there are **`r ret$length`** colleges in the dataset. Among them, there are **`r ret$num_public`** public schools and **`r ret$num_private`** private schools. There are **`r ret$num_for_profit`** schools run for profits. The average tuition for in-state students is **$`r ret$avg_instate_tuition`**  and for out-state students is **$`r ret$avg_out_of_state_tuition`**. The average tuition of public colleges for in-state students is **$`r ret$avg_instate_public`**  and those for private colleges is **$`r ret$avg_instate_private`**. The average tuition of public colleges for out-state students is **$`r ret$avg_outstate_public`** and for private schools is **$`r ret$avg_outstate_private`**. The university that has the highest in-state tuition is **`r ret$most_expensive_instate`** and The university that havs the highest out-state tuition is **`r ret$most_expensive_outstate`**. 




## Chart

### Chart 1

```{r, echo=FALSE}
point_plot(df)
```

### Chart 2 
```{r, echo=FALSE}
filtered <- filter(df, !is.na(room_and_board))
hex_plot(filtered)

```

### Chart 3
```{r, echo=FALSE}
bin_plot(df)
```

